---
title: "Hello R"
author: "Precious Merenu"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 variables. The three variables are: dataset, x for x-values, and y for y-values. 

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}

star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

First let's plot the data in the star dataset:

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```
And next calculate the correlation between `x` and `y` in this dataset:

```{r}


circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5
Finally, we are  plot all datasets at once and calculate their summary correlation coefficients utilizing a technique called facetting.

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
 geom_point()+
 facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
 theme(legend.position = "none")

```
And use the group_by function to generate all the summary correlation coefficients.
```{r}

datasaurus_dozen %>%
 group_by(dataset) %>%
 summarize(r = cor(x, y))
```